Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
fb <-read.delim('pseudo_facebook.tsv')
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)
qplot(data = fb, x=dob_day)+
  scale_x_continuous(breaks = 1:31)+
  facet_wrap(~dob_month, ncol=3)
```

***

#### What are some things that you notice about this histogram?
Response:
1st is much greater than the others.
***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:


***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:
post: I was on Facebook for 5 years.
#### How many of your friends do you think saw that post?
Response:
estimate audience:50
#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:
percentage:20%
***

### Perceived Audience Size
Notes:
4 times, should be 200
***
### Faceting
Notes:

```{r Faceting}
facet_wrap(~dob_month, ncol = 4)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:
only the 1st of Jan was extremely large, others are similar.
***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:
bad, exterme
***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(data = fb,  x = friend_count, xlim = c(0,1000))
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
qplot(data = fb, x = friend_count, binwidth = 25)+
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))  +
  facet_wrap(~gender)
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(data = subset(fb, !is.na(gender)),x = friend_count, binwidth = 25) +
  scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,50))+
  facet_wrap(~gender)

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
by(fb$friend_count, fb$gender,summary)
```

#### Who on average has more friends: men or women?
Response:
Women

#### What's the difference between the median friend count for women and men?
Response:
22
#### Why would the median be a better measure than the mean?
Response:
robustic
***

### Tenure
Notes:

```{r Tenure}
qplot(data = fb, x = tenure, binwidth = 182.5,
      color = I('black'), fill = I('#099DD9'))+
  scale_x_continuous(breaks = seq(1,3000,182.5), limits = c(1,3000))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(data = fb, x = tenure/365, binwidth = 0.25,
      color = I('black'), fill = I('#099DD9'))+
  scale_x_continuous(breaks = seq(1,7,1), limits = c(1,7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(data = fb, x = tenure/365, binwidth = 0.25,
      color = I('black'), fill = I('#099DD9'),
      xlab = 'tenure by year',
      ylab = 'number of users')+
  scale_x_continuous(breaks = seq(1,7,1), limits = c(1,7))
```

***

### User Ages
Notes:

```{r User Ages}
qplot(data = fb, x = age, binwidth = 1,
      color = I('black'), fill = I('#099DD9'),
      xlab = 'age',
      ylab = 'number of users')+
  scale_x_continuous(breaks = seq(1,100,10), limits = c(1,100))
ggplot(aes(x=age),data = fb)+
  geom_histogram(color = 'grey', binwidth = 1, fill = I('#1AAD19'))+
  scale_x_continuous(limits = c(0,100),breaks = seq(0,100,10))
```

#### What do you notice?
Response:
most of the users are young adults.
***

### The Spread of Memes
Notes:
the Memes always come back after a period of time.
***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:
```{r}
library(ggplot2)
p1 <- qplot(data = fb, x = friend_count, color = I('black'),fill = I('#1AAD19'), binwidth = 10)+
  scale_x_continuous(limits = c(0,1000),breaks = seq(0,1500,100))

p2 <- qplot(data = fb, x = log10(friend_count+1), color = I('black'),fill = I('#1AAD19'), binwidth = 0.1)
  #scale_x_log10(limits = c(0,5),breaks = seq(0,5,1))

p3 <- qplot(data = fb, x = sqrt(friend_count), color = I('black'),fill = I('#1AAD19'), binwidth = 1)

library(gridExtra)
grid.arrange(p1,p2,p3,ncol = 1)
```


***

### Add a Scaling Layer
Notes:
Show in New WindowClear OutputExpand/Collapse Output
	
`stat_bin()` using `bins = 30`. Pick better value with `binwidth`.

Show in New WindowClear OutputExpand/Collapse Output
	
`stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
	
Removed 2951 rows containing non-finite values (stat_bin).

Modify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output
	
Removed 2951 rows containing non-finite values (stat_bin).

Show in New WindowClear OutputExpand/Collapse Output
	
Removed 2949 rows containing non-finite values (stat_bin).

Modify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output
facebook$gender: female
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0      37      96     242     244    4923 
--------------------------------------- 
facebook$gender: male
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
      0      27      74     165     182    4917 
Show in New WindowClear OutputExpand/Collapse Output
	
Removed 79 rows containing non-finite values (stat_bin).
Removed 1 rows containing missing values (geom_bar).

Modify Chunk OptionsRun All Chunks AboveRun Current ChunkModify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output
	
Removed 43558 rows containing non-finite values (stat_bin).

Modify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output
	
Removed 43558 rows containing non-finite values (stat_bin).

```{r Add a Scaling Layer}
p1 = ggplot(aes(x=friend_count),data = fb)+
  geom_histogram()#(binwidth = 100, color = 'white', fill = I('#1AAD19'))

p2 = p1 + scale_x_log10()
p3 = p1 + scale_x_sqrt()

grid.arrange(p1,p2,p3)
```

***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = www_likes), data = subset(fb,!is.na(gender)))+
  geom_freqpoly(aes(color = gender),binwidth = 30)+
  #scale_x_continuous()+
  scale_x_log10()
  #scale_x_continuous(limits = c(0,800))
  #scale_y_continuous(limits = c(0,0.04))
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
ggplot(aes(x = www_likes), data = subset(fb,!is.na(gender)))+
  geom_freqpoly(aes(color = gender),binwidth = 30)+
  #scale_x_continuous()+
  scale_x_log10()
```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender, y = friend_count, data = subset(fb,!is.na(gender)),geom = 'boxplot')
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
ggplot(aes(x = gender, y = friend_count),data = subset(fb,!is.na(gender)))+
  geom_boxplot()+
  #scale_y_continuous(limits = c(0,1000))
  coord_cartesian(ylim = c(0,1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
ggplot(aes(x = gender, y = friend_count),data = subset(fb,!is.na(gender)))+
  geom_boxplot()+
  #scale_y_continuous(limits = c(0,1000))
  coord_cartesian(ylim = c(0,250))
```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
ggplot(aes(x=gender, y= friendships_initiated), data = subset(fb,!is.na(gender)))+
  geom_boxplot()+
  coord_cartesian(ylim = c(0,150))

by(fb$friendships_initiated,fb$gender,summary)
```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
summary(fb$mobile_likes>0)

fb$mobile_check_in <-NA
fb$mobile_check_in <- ifelse(fb$mobile_likes>0 , TRUE,FALSE)
fb$mobile_check_in <- fb$mobile_check_in>0
summary(fb$mobile_check_in)
percent <-sum(fb$mobile_check_in)/length(fb$mobile_check_in)
percent
```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!