Lesson 5
========================================================
```{r}
library(ggplot2)
library(dplyr)

```

### Multivariate Data
Notes:
```{r}
fb <- read.delim('pseudo_facebook.tsv')
```

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:
什么情况下需要用到stat_summary？起什么作用？什么情况下用stat = 'summary'？fun.y?

```{r Third Qualitative Variable}
age_gender <- group_by(subset(fb,!is.na(gender)&!is.na(age)),age,gender)
pf.fc_by_age_gender <- summarise(age_gender,
                                 mean_friend_count = mean(friend_count),
                                 median_friend_count = median(friend_count),
                                 n = n())
ungroup(age_gender)
pf.fc_by_age_gender <- arrange(pf.fc_by_age_gender,age)

age_gender <- group_by(subset(fb,!is.na(gender)&!is.na(age)),age,gender)
pf.fc_by_age_gender <- fb %>%
  filter(!is.na(gender))%>%
  group_by(age,gender)%>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n())%>%
  ungroup()%>%
  arrange(age)


ggplot(aes(gender,age), data = subset(fb,!is.na(gender)))+
  geom_boxplot()+
  stat_summary(fun.y = mean,geom = 'point',shape = 4)

ggplot(aes(age,friend_count), data = subset(fb,!is.na(gender)))+
  geom_line(aes(color = gender),stat = 'summary',fun.y = median)
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(aes(age, median_friend_count), data = pf.fc_by_age_gender)+
  geom_line(aes(color = gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:
mutate - 添加新的一列
***
```{r}
library(tidyr)
tidy_fc_by_age_gender <- spread(subset(pf.fc_by_age_gender,select = c(age,gender,median_friend_count)),gender,median_friend_count)%>%
mutate(ratio = female/male)
```

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(age, ratio), data = tidy_fc_by_age_gender)+
  geom_line()+
  geom_hline(yintercept = 1, linetype = 2, alpha = 0.4)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
fb$year_joined <- floor(2014 - fb$tenure/365)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
fb$year_joined.bucket <- cut(fb$year_joined,c(2004,2009,2011,2012,2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(aes(age,friend_count), data = subset(fb,!is.na(year_joined.bucket)))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(age,friend_count), data = subset(fb,!is.na(year_joined.bucket)))+
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)+
  geom_line(stat = 'summary', fun.y = mean, linetype = 3)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(fb,!is.na(fb$tenure) & fb$tenure != 0 & fb$friend_count != 0),summary(friend_count/tenure))

with(subset(fb, tenure >=1),summary(friend_count/tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(aes(10 * round(tenure/10), friendships_initiated/tenure), data = subset(fb,tenure >0))+
  #geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)+
  geom_smooth(aes(color = year_joined.bucket))
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:
```{r}
yo <- read.csv('yogurt.csv')
yo$id <- factor(yo$id)
```

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
ggplot(aes(price), data = yo)+
  geom_histogram()
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
yo$all.purchases <- yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry

yo <- transform(yo, strawberry + blueberry + pina.colada + plain + mixed.berry)
```

***

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(aes(time, price), data = yo)+
  geom_jitter(alpha = 0.1)
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(666)
id.samples <- sample(levels(yo$id),20)

ggplot(aes(time, price), data = subset(yo, id %in% id.samples))+
  facet_wrap(~id)+
  geom_line()+
  geom_point(aes(size = all.purchases),alpha =0.3)
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:
无法安装GGally包，总是安装到C盘，提示：

> 'D:\Program' 不是内部或外部命令，也不是可运行的程序
或批处理文件。
Warning in install.packages :
  running command '"D:/Program Files/R/R-3.3.2/bin/x64/R" CMD INSTALL -l "D:\Program Files\R\R-3.3.2\library" C:\Users\HP\AppData\Local\Temp\Rtmp8YSdD4/downloaded_packages/GGally_1.3.1.tar.gz' had status 1
Warning in install.packages :
  installation of package ‘GGally’ had non-zero exit status

The downloaded source packages are in
	‘C:\Users\HP\AppData\Local\Temp\Rtmp8YSdD4\downloaded_packages’
	
***
```{r}
library(GGally)
theme_set(theme_minimal(20))

set.seed(666)
pf_subset <- fb[,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
library(reshape2)
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!



# Practices

##1. histogram with facet and color
```{r}
data("diamonds")
ggplot(aes(log(price)), data = diamonds)+
  geom_histogram(aes(color=cut))+
  facet_wrap(~color)+
  scale_color_brewer(type = 'qual')
```

## 2. price and cut with color
```{r}
ggplot(aes(table,price), data= diamonds)+
  geom_point(aes(color=cut))
```

## 3. typical table range of ideal cut?
```{r}
ggplot(aes(cut,table),data = diamonds)+
  geom_boxplot()+
  coord_cartesian(ylim = c(50,70))

summarise()
```

## 4.Diamond price vs. volume by clarity   
# question:how to limit the x axis to 99% percent?
```{r}
diamonds$volume <- diamonds$x*diamonds$y*diamonds$z
ggplot(aes(volume, price), data=diamonds)+
  geom_point(aes(color=clarity))+
  scale_y_log10()+
  scale_x_continuous(limits = c(0,quantile(diamonds$volume,0.99)))
```

## 5. Proportion of friendship initiated
```{r}
pf$prop_initiated <- pf$friendships_initiated/pf$friend_count
```

## 6. prop_initiated and tenure.
```{r}
ggplot(aes(tenure, prop_initiated,color=year_joined.bucket),data = subset(pf,!is.nan(prop_initiated)))+
  geom_line(stat = 'summary',fun.y=median,na.rm = TRUE)
```

## 7. smooth the last plot
```{r}
ggplot(aes(tenure, prop_initiated,color=year_joined.bucket),data = subset(pf,!is.nan(prop_initiated)))+
  geom_line(stat = 'summary',fun.y=median,na.rm = TRUE)+
  geom_smooth()
```

## 9. what is the mean of prop_initiated for the group of 2012~2014?
```{r}
year_bucket<-group_by(subset(pf,!is.nan(prop_initiated)),year_joined.bucket)

summarise(year_bucket,
          mean = mean(prop_initiated))

       
```

## 10. group and facet of diamonds
```{r}
ggplot(aes(cut,price),data=diamonds)+
  geom_jitter(aes(color=color))+
  facet_wrap(~clarity)+
  scale_color_brewer(type='div')
```

# Diamonds
## scatter plot
```{r}
ggplot(aes(carat,price),data=diamonds)+
  geom_point()+
  scale_x_continuous(limits = c(0,quantile(diamonds$carat,0.99)))+
  scale_y_continuous(limits = c(0,quantile(diamonds$price,0.99)))
```

