Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
fb <-read.delim('pseudo_facebook.tsv')
ggplot(aes(age,friend_count), data = fb)+
  geom_jitter(alpha = 0.05)+
  xlim(13,90)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(age,friend_count), data = fb)+
  geom_jitter(alpha = 0.05)+
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(age,friend_count), data = fb)+
  geom_jitter(alpha = 0.01,position = position_jitter(h = 0))+
  xlim(13,90)+
  coord_trans(y='sqrt')

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(age,friend_count), data = fb)+
  geom_jitter(alpha = 0.01,position = position_jitter(h = 0))+
  xlim(13,90)+
  coord_trans(y='sqrt')
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(fb,aes(age,friendships_initiated))+
  geom_jitter(alpha = 0.01)+
  coord_trans(limy = c(0,2000))
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
age_groups <- group_by(fb,age)
fc_by_age <- summarise(age_groups,
                       friend_count_mean = mean(friend_count),
                       friend_count_median = median(friend_count),
                       n = n())

```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(age,friend_count_mean),data = fc_by_age)+
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(age,friend_count), data = fb)+
  geom_point(alpha = 0.01,
             position = position_jitter(h = 0),
             color = 'orange')+
  xlim(13,90)+
  coord_trans(y = 'sqrt')+
  geom_line(stat = 'summary',fun.y = mean)+
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs=.1 ),color = 'red', linetype = 2)+
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs=.9 ), color = 'green')+
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs=.5 ), color = 'purple')
```

#### What are some of your observations of the plot?
Response:
young people have more friend counts, although the friend count for people above 70 is higher than those between 30 and 70.
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(fb$age,fb$friend_count, alternative = 'two.sided', method = 'pearson', conf.level = .95)
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(fb,age<=60), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
fb <- read.delim('pseudo_facebook.tsv')
ggplot(aes(likes_received, www_likes_received), data = fb)+
  geom_point(alpha = 0.1)+
  coord_cartesian(xlim = c(0,10000),ylim = c(0,10000))
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(likes_received, www_likes_received), data = fb)+
  geom_point(alpha = 0.1)+
  xlim(0,quantile(fb$likes_received,.95))+
  ylim(0,quantile(fb$www_likes_received,.95))+
  geom_smooth(method = 'lm', color = 'yellow')
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
cor.test(fb$likes_received, fb$www_likes_received)
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data("Mitchell")
?Mitchell
```

Create your plot!

```{r Temp vs Month}
names(Mitchell)

ggplot(aes(Month, Temp), data = Mitchell)+
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month,Mitchell$Temp)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(Month%%12, Temp), data = Mitchell)+
  geom_point()

ggplot(aes(Month, Temp), data = Mitchell)+
  geom_point()+
  scale_x_continuous(breaks = seq(0,203,12))
```

***

### A New Perspective
```{r}
ggplot(aes(Month, Temp), data = Mitchell)+
  geom_point()+
  scale_x_continuous(breaks = seq(0,203,12))+
  xlim(0,24)

install.packages('energy')
library(energy)
dcor.ttest(Mitchell$Month,Mitchell$Temp)
```

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
fb$age_with_month <- fb$age + (1-fb$dob_month/12)

```

***

### Age with Months Means

```{r Age with Months Means}
library(dplyr)
age_with_month_groups <- group_by(fb,age_with_month)
fb.fc_by_age_month <- summarise(age_with_month_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n())
fb.fc_by_age_month <- arrange(fb.fc_by_age_month, age_with_month)


```

Programming Assignment
```{r Programming Assignment}
ggplot(aes(age_with_month, friend_count_mean), data = subset(fb.fc_by_age_month, age_with_month <71))+
  geom_line()
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:
there can be many hidden correlation among the variables in a data set, we need to find out and describe them by statistical models like Pearson test , or by observing the graphs we create.
***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!


#Problem set
## Diamonds, price and x
```{r}
library(ggplot2)
d <- diamonds

ggplot(aes(price,x), data = d)+
  geom_point()
```

## coorelation
```{r}
cor.test(d$price,d$x)
cor.test(d$price,d$y)
cor.test(d$price,d$z)
```

## Price and depth plot
```{r}
ggplot(aes(depth,price),data = d)+
  geom_point()

cor.test(d$depth, d$price)
```

## price and carat.
```{r}
ggplot(aes(carat, price), data = d)+
  geom_point()+
  xlim(0,quantile(d$carat,.99))+
  ylim(0,quantile(d$price,.99))
```

## price and volume.
```{r}
d$volume <- d$x * d$y * d$z

ggplot(aes(volume, price), data = d)+
  geom_point()
```

## subset
```{r}
d1 <- subset(d,volume != 0 & volume <800)
cor.test(d1$price, d1$volume)
```

## adjust the price and volume.
```{r}
ggplot(aes(volume, price), data = d)+
  geom_point()+
  xlim(0,800)+
  geom_smooth(method = 'lm', formula = y~x, size = 1)
```

## average price by clearity.
```{r}
library(dplyr)
clarity_group <- group_by(d,clarity)
diamondsByClarity <- summarise(clarity_group,
          mean_price = mean(price),
          median_price = median(price),
          min_price = min(price),
          max_price = max(price),
          n = n())
#diamondsByClarity <- sort(diamondsByClarity, clarity_group)
```

##average price histgram.
```{r}
library(gridExtra)
diamonds_by_clarity <- group_by(d, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color <- group_by(d, color)
diamonds_mp_by_color <- summarise(diamonds_by_color, mean_price = mean(price))

ggplot(aes(diamonds_by_clarity, mean_price), data = diamonds_mp_by_clarity)+
  geom_histogram()
ggplot(aes(diamonds_by_color, mean_price), data = diamonds_mp_by_color)+
  geom_histogram()

p1
p2
#grid.arrange(p1,p2,nrow =1)
```
##gapminder data.
```{r}
smoking <- read.csv('smoking.csv')
ggplot(aes(country,X2002), data = smoking)+
  geom_point()
ggplot(aes(country), data = smoking)+
  geom_freqpoly(stat="count")
```

